From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-06-20 article/article.tex
Readme file

\begin{figure}[t]
    \includegraphics[width=0.48\textwidth]{images/search_space_3.png}
    \caption{Modularity search space of an \textit{E. coli} metabolic network.
 Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
  The inset (top) demonstrates the landscape of the high modularity region.
  Figure generated with the software of Good \textit{et al.} \cite{good2010performance}.}
    \label{fig:modular_search_space}
\end{figure}

@@

The work by \cite{good2010performance} forms the basis of the motivation of the approach taken here.
In this study, the authors discovered that the modularity search space for many real-world networks contains a huge number of high value solutions.
Each of these solution partitions are extremely close to the global maxima, making it both difficult to find the optimal value of $Q$ and difficult to argue that the highest scoring partition is the ``true'' community structure.
This fact is visually demonstrated with the software from \cite{good2010performance} in Figure \ref{fig:modular_search_space}, which shows the modularity search space of an \textit{E. coli} metabolic network reconstruction \cite{GuimeraNature2005}.
The similarity between the partitions is compared with the variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear} \footnote{The reader should note that axis on these plots are a result of the dimensionality reduction performed by curvilinear component analysis \cite{demartines1997curvilinear} and, therefore, have no natural interpretation.}.

>>>>

% \begin{figure}[t]
%     \includegraphics[width=0.48\textwidth]{images/search_space_3.png}
%     \caption{Modularity search space of an \textit{E. coli} metabolic network.
%  Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
%   The inset (top) demonstrates the landscape of the high modularity region.
%   Figure generated with the software of Good \textit{et al.} \cite{good2010performance}.}
%     \label{fig:modular_search_space}
% \end{figure}

@@

The work by \cite{good2010performance} forms the basis of the motivation of the approach taken here.
In this study, the authors discovered that the modularity search space for many real-world networks contains a huge number of high value solutions.
Each of these solution partitions are extremely close to the global maxima, making it both difficult to find the optimal value of $Q$ and difficult to argue that the highest scoring partition is the ``true'' community structure.
% This fact is visually demonstrated with the software from \cite{good2010performance} in Figure \ref{fig:modular_search_space}, which shows the modularity search space of an \textit{E. coli} metabolic network reconstruction \cite{GuimeraNature2005}.
% The similarity between the partitions is compared with the variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear} \footnote{The reader should note that axis on these plots are a result of the dimensionality reduction performed by curvilinear component analysis \cite{demartines1997curvilinear} and, therefore, have no natural interpretation.}.
